`gosset`: An R package for analysis and synthesis of ranking data in agricultural

### 2022-06-25 inst/paper/paper.Rmd
example1

Than we prepare the matrix to compute the rainfall indices using the function `rainfall()` from package climatrends.

```{r chirps3, message=FALSE, eval=FALSE, echo=TRUE}
dates <- c(min(covar[, "planting_date"]),
           max(covar[, "planting_date"]) + 70)

To be linket to covariates, the rankings should be coerced to 'grouped rankings'. For this we used the function `group()` from PlackettLuce. We retain the ranking corresponding to yield.

```{r , message=FALSE, eval=TRUE, echo=TRUE}
R <- vector(mode = "list", length = length(traits))

  R[[i]] <- rank_numeric(data = dat_i,
                         items = "item",
                         input = "rank",
                         id = "id",
                         ascending = TRUE,
                         group = TRUE)
}
```

@@

```{r , message=FALSE, eval=TRUE, echo=TRUE}

R <- R[[9]]

pld <- cbind(R, nicabean_temp_ind)

pl <- pltree(R ~ .,
             alpha = .6,
             data = pld)
```

The following is an example of the plot made with the function ``plot`` in the gosset package.
```{r , message=FALSE, eval=FALSE, echo=TRUE}
plot(pl)

```
!["Plackett-Luce tree plot with gosset function *plot*"](pltree_01.png)

We can use the function ``reliability`` to compute the reliability of the evaluated common bean
varieties in each of the resulting nodes of the Plackett-Luce tree (Table 3).

```{r rel1, message=FALSE, eval=TRUE, echo=FALSE}
# nicabean_rel <- reliability(pl, ref = "Amadeus 77")
# 
# kable(t(nicabean_rel), col.names = c("node 2", "node 3"), caption = "Reliability of evaluated varieties
#       in each of the resulting nodes of the Plackett-Luce tree")

With the function ``crossvalidation`` we can validate the model.

```{r, message=FALSE, eval=TRUE, echo=FALSE}
nb_cv <- crossvalidation(R ~ .,
                         alpha = .6,
                         data = pld)

```
```{r cv, message=FALSE, eval=TRUE, echo=FALSE}

kable(nb_cv$coeffs[,c(1:4, 7, 8)], caption = "Results of 10-fold random cross-validation")

>>>>

Than we prepare the matrix to compute the rainfall indices using the function `rainfall()` from package climatrends. We compute rainfall indices for the first 45 days after planting.

```{r chirps3, message=FALSE, eval=TRUE, echo=TRUE}
newnames <- dimnames(chirps)[[2]]
newnames <- gsub("chirps-v2.0.", "", newnames)
newnames <- gsub("[.]", "-", newnames)

dimnames(chirps)[[2]] <- newnames

rain <- rainfall(chirps, day.one = covar$planting_date, span = 45)
```

To be linked to covariates, the rankings should be coerced to a 'grouped_rankings' object. For this we use the function `group()` from PlackettLuce. We retain the ranking corresponding to yield.

```{r grouped_ranking, message=FALSE, eval=TRUE, echo=TRUE}
G <- which(grepl("Yield", traits))

G <- group(R[[G]], index = 1:length(R[[G]]))
```

@@

```{r pltree, message=FALSE, eval=TRUE, echo=TRUE}
pldG <- cbind(G, rain)

tree <- pltree(G ~ Rtotal, data = pldG, alpha = 0.1)
```

The following is an example of the plot made with the function `plot()` in the gosset package.

```{r , message=FALSE, eval=TRUE, echo=TRUE, fig.width=4, fig.height=4, fig.cap="Plackett-Luce tree of bean yield in on-farm trials"}
plot(tree)
```

We can use the function `reliability()` to compute the reliability of the evaluated common bean
varieties in each of the resulting nodes of the Plackett-Luce tree (Table 3).

```{r rel1, message=FALSE, eval=TRUE, echo=FALSE}
rel <- reliability(tree, ref = "Amadeus 77")
```
